Determining the alternatives for scalar implicature

### 2016-01-31 Paper/Paper.Rmd
fixed equation reference (used \tag{1} in 7383 .. 7383)
fixed van tiel reference, removed table 1 reference and replaced with hardcoded 'Table 1'

$$p_{L_1}(m \mid u) \propto p_{S_1} (u \mid m) p(m) \label{eq:rsa}$$

@@

Experiment 3 was conducted to measure pragmatic judgments---$p_{L_1}(m \mid u)$ in Equation \ref{eq:rsa}. As in Experiment 1, we include several conditions to test inferences in the presence of different alternative sets. In the two alternatives condition, participants made judgments for items included in the entailment scales. In the four alternatives condition, participants made judgments for the entailment items and also the top two alternatives elicited for each scale in Experiment 2. Including two conditions with differing alternatives allowed us to rule out the potential effects of having a larger set of alternatives during the pragmatic judgment elicitation and also provided two sets of human judgments to compare with model predictions.\footnote{Note that alternatives in the four alternatives condition were chosen on the basis of Experiment 2, which was run chronologically after the two alternatives condition; both pragmatic listener experiments are grouped together for simplicity in reporting.}

@@

Using literal listener data from Experiment 1, we conducted a set of simulations with the RSA model. Each simulation kept the model constant, fitting the choice parameter $\alpha$ as a free parameter, but used a set of alternatives to specify the scale over which predictions were computed. We considered four different alternative sets, with empirical measurements corresponding to those shown in Table \ref{fig:allScalesTable): 1) the two alternatives in the classic entailment scales, 2) those two alternatives with the addition of a generic negative alternative, 3) the expanded set of four alternatives tested in Experiment 1, and 4) the expanded set of five alternatives tested in Experiment 1.

Model fit with human judgments was significantly improved by the inclusion of alternatives beyond the entailment items (Table \ref{fig:xtable}). The two alternatives model contained only entailment items, which, under classic accounts, should be sufficient to generate implicature, but fit to data was quite poor with these items. The addition of a generic negative element produced some gains in performance, but much higher performance was found when we included four and five alternatives, with the alternatives derived empirically for the specific scale we used. An example fit for the five-alternative model is shown in Figure \ref{fig:fiveAltsScatter}.

@@

In our current work, we used the rational speech act framework to investigate the set of alternatives that best allowed the model to predict pragmatic judgments across a series of different scales. We found that the best predictions came when a range of scale-dependent negative and neutral alternatives were added to the implicature computation, suggesting the importance of considering non-entailment alternatives. This work builds on previous investigations, reinforcing the claim that negative alternatives are critical for understanding implicature [@franke2014], and replicates and extends findings that different lexical scales produce strikingly different patterns of inference [@vantiel2015].

>>>>

$$p_{L_1}(m \mid u) \propto p_{S_1} (u \mid m) p(m) \tag{1}$$

@@

Experiment 3 was conducted to measure pragmatic judgments---$p_{L_1}(m \mid u)$ in Equation $(1)$. As in Experiment 1, we include several conditions to test inferences in the presence of different alternative sets. In the two alternatives condition, participants made judgments for items included in the entailment scales. In the four alternatives condition, participants made judgments for the entailment items and also the top two alternatives elicited for each scale in Experiment 2. Including two conditions with differing alternatives allowed us to rule out the potential effects of having a larger set of alternatives during the pragmatic judgment elicitation and also provided two sets of human judgments to compare with model predictions.\footnote{Note that alternatives in the four alternatives condition were chosen on the basis of Experiment 2, which was run chronologically after the two alternatives condition; both pragmatic listener experiments are grouped together for simplicity in reporting.}

@@

Using literal listener data from Experiment 1, we conducted a set of simulations with the RSA model. Each simulation kept the model constant, fitting the choice parameter $\alpha$ as a free parameter, but used a set of alternatives to specify the scale over which predictions were computed. We considered four different alternative sets, with empirical measurements corresponding to those shown in Figure \ref{fig:allScalesTable}: 1) the two alternatives in the classic entailment scales, 2) those two alternatives with the addition of a generic negative alternative, 3) the expanded set of four alternatives tested in Experiment 1, and 4) the expanded set of five alternatives tested in Experiment 1.

Model fit with human judgments was significantly improved by the inclusion of alternatives beyond the entailment items (Table 1). The two alternatives model contained only entailment items, which, under classic accounts, should be sufficient to generate implicature, but fit to data was quite poor with these items. The addition of a generic negative element produced some gains in performance, but much higher performance was found when we included four and five alternatives, with the alternatives derived empirically for the specific scale we used. An example fit for the five-alternative model is shown in Figure \ref{fig:fiveAltsScatter}.

@@

In our current work, we used the rational speech act framework to investigate the set of alternatives that best allowed the model to predict pragmatic judgments across a series of different scales. We found that the best predictions came when a range of scale-dependent negative and neutral alternatives were added to the implicature computation, suggesting the importance of considering non-entailment alternatives. This work builds on previous investigations, reinforcing the claim that negative alternatives are critical for understanding implicature [@franke2014], and replicates and extends findings that different lexical scales produce strikingly different patterns of inference [@vantiel2014].

### 2016-01-31 Paper/Paper.tex
fixed equation reference (used \tag{1} in 7383 .. 7383)
fixed van tiel reference, removed table 1 reference and replaced with hardcoded 'Table 1'

\[p_{L_1}(m \mid u) \propto p_{S_1} (u \mid m) p(m) \label{eq:rsa}\]

@@

Experiment 3 was conducted to measure pragmatic
judgments---\(p_{L_1}(m \mid u)\) in Equation \ref{eq:rsa}. As in
Experiment 1, we include several conditions to test inferences in the
presence of different alternative sets. In the two alternatives
condition, participants made judgments for items included in the
entailment scales. In the four alternatives condition, participants made
judgments for the entailment items and also the top two alternatives
elicited for each scale in Experiment 2. Including two conditions with
differing alternatives allowed us to rule out the potential effects of
having a larger set of alternatives during the pragmatic judgment
elicitation and also provided two sets of human judgments to compare
with model
predictions.\footnote{Note that alternatives in the four alternatives condition were chosen on the basis of Experiment 2, which was run chronologically after the two alternatives condition; both pragmatic listener experiments are grouped together for simplicity in reporting.}

@@

Using literal listener data from Experiment 1, we conducted a set of
simulations with the RSA model. Each simulation kept the model constant,
fitting the choice parameter \(\alpha\) as a free parameter, but used a
set of alternatives to specify the scale over which predictions were
computed. We considered four different alternative sets, with empirical
measurements corresponding to those shown in Table
\textbackslash{}ref\{fig:allScalesTable): 1) the two alternatives in the
classic entailment scales, 2) those two alternatives with the addition
of a generic negative alternative, 3) the expanded set of four
alternatives tested in Experiment 1, and 4) the expanded set of five
alternatives tested in Experiment 1.

Model fit with human judgments was significantly improved by the
inclusion of alternatives beyond the entailment items (Table
\ref{fig:xtable}). The two alternatives model contained only entailment
items, which, under classic accounts, should be sufficient to generate
implicature, but fit to data was quite poor with these items. The
addition of a generic negative element produced some gains in
performance, but much higher performance was found when we included four
and five alternatives, with the alternatives derived empirically for the
specific scale we used. An example fit for the five-alternative model is
shown in Figure \ref{fig:fiveAltsScatter}.

@@

In our current work, we used the rational speech act framework to
investigate the set of alternatives that best allowed the model to
predict pragmatic judgments across a series of different scales. We
found that the best predictions came when a range of scale-dependent
negative and neutral alternatives were added to the implicature
computation, suggesting the importance of considering non-entailment
alternatives. This work builds on previous investigations, reinforcing
the claim that negative alternatives are critical for understanding
implicature (Franke, 2014), and replicates and extends findings that
different lexical scales produce strikingly different patterns of
inference ({\textbf{???}}).

>>>>

\[p_{L_1}(m \mid u) \propto p_{S_1} (u \mid m) p(m) \tag{1}\]

@@

Experiment 3 was conducted to measure pragmatic
judgments---\(p_{L_1}(m \mid u)\) in Equation \((1)\). As in Experiment
1, we include several conditions to test inferences in the presence of
different alternative sets. In the two alternatives condition,
participants made judgments for items included in the entailment scales.
In the four alternatives condition, participants made judgments for the
entailment items and also the top two alternatives elicited for each
scale in Experiment 2. Including two conditions with differing
alternatives allowed us to rule out the potential effects of having a
larger set of alternatives during the pragmatic judgment elicitation and
also provided two sets of human judgments to compare with model
predictions.\footnote{Note that alternatives in the four alternatives condition were chosen on the basis of Experiment 2, which was run chronologically after the two alternatives condition; both pragmatic listener experiments are grouped together for simplicity in reporting.}

@@

Using literal listener data from Experiment 1, we conducted a set of
simulations with the RSA model. Each simulation kept the model constant,
fitting the choice parameter \(\alpha\) as a free parameter, but used a
set of alternatives to specify the scale over which predictions were
computed. We considered four different alternative sets, with empirical
measurements corresponding to those shown in Figure
\ref{fig:allScalesTable}: 1) the two alternatives in the classic
entailment scales, 2) those two alternatives with the addition of a
generic negative alternative, 3) the expanded set of four alternatives
tested in Experiment 1, and 4) the expanded set of five alternatives
tested in Experiment 1.

Model fit with human judgments was significantly improved by the
inclusion of alternatives beyond the entailment items (Table 1). The two
alternatives model contained only entailment items, which, under classic
accounts, should be sufficient to generate implicature, but fit to data
was quite poor with these items. The addition of a generic negative
element produced some gains in performance, but much higher performance
was found when we included four and five alternatives, with the
alternatives derived empirically for the specific scale we used. An
example fit for the five-alternative model is shown in Figure
\ref{fig:fiveAltsScatter}.

@@

In our current work, we used the rational speech act framework to
investigate the set of alternatives that best allowed the model to
predict pragmatic judgments across a series of different scales. We
found that the best predictions came when a range of scale-dependent
negative and neutral alternatives were added to the implicature
computation, suggesting the importance of considering non-entailment
alternatives. This work builds on previous investigations, reinforcing
the claim that negative alternatives are critical for understanding
implicature (Franke, 2014), and replicates and extends findings that
different lexical scales produce strikingly different patterns of
inference (Tiel, 2014).
